Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-09-06 paper/ms.tex
Add Federico comments

\subsection{Semi-Analytic Model}
We also developed a simple semi-analytic model of a bar-disk-halo system. This
exercise demonstrates that our proposed mechanism follows from a few simplistic
assumptions. Our method follows closely the one developed in
\citet{2022MNRAS.513..768C}. We model the bar-disk-halo system with three
components: a dark matter Hernquist halo \citep{1990ApJ...356..359H}, a
Miyamoto-Nagai disk \citep{1975PASJ...27..533M}, and a pure quadrupole bar
described in \citet{2022MNRAS.513..768C}. The bar and disk components are just
described by their potential, but we integrate the trajectories of test
particles drawn from a Hernquist halo. Note that we do not include the
interactions between these test particles, and so this model is not
self-consistent. We give our chosen parameter values in Appendix~\ref{app:sam}.

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed at each timestep. Since the radius of corotation
\RCR{} is a parameter in the bar model from \citet{2022MNRAS.513..768C}, we
allow the moment of inertia of the bar to vary with ${\RCR}^2$. To be more
precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing
$I_6=8$ is a good approximation to our fiducial disk model.

>>>>

\subsection{Semi-Analytic Model}
We also developed a simple semi-analytic model of a bar-disk-halo system. This
exercise demonstrates that our proposed mechanism follows from a few simple
assumptions. Our method follows closely the one developed in
\citet{2022MNRAS.513..768C}. We model the bar-disk-halo system with three
components: a dark matter \citet{1990ApJ...356..359H} halo, a
\citet{1975PASJ...27..533M} disk, and a pure quadrupole bar
described in \citet{2022MNRAS.513..768C}. The bar and disk components are just
described by their potential, but we integrate the trajectories of test
particles drawn from a Hernquist halo. Note that we do not include the
interactions between these test particles, and so this model is not
self-consistent. We give our chosen parameter values in Appendix~\ref{app:sam}.

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed at each timestep. Since the radius of corotation
\RCR{} is a parameter in the bar model from \citet{2022MNRAS.513..768C}, we
allow the moment of inertia of the bar to vary with ${\RCR}^2$. To be more
precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing
$I_6=8$ is a good approximation to our fiducial disk model. In code units, the
moment of inertia of the SMUGGLE bar (i.e., the particles classified as being in
the bar) is about $2$. This is a factor of $4$ smaller than our fiducial value
of $I_6=8$, but this is probably due to the fact that the bar does not really
rotate as a solid body.
